Ripple Protocol Consensus Algorithm Review

### 2015-05-11 paper.tex
close to finished

Unlike Bitcoin, transactions increment and decrement account balances; they do
not directly consume the output of other transactions. Transactions are also
used to setup and modify trustlines. To prevent replay attacks, accounts and
transactions have sequence numbers; a transaction is only valid if the Sequence
number is exactly one greater than the last-valided transaction from the same
account. Additionally an optional AccountTxnID field is available for use
within transactions; the transaction is only valid if the sending account's
previously-sent transaction matches the provided hash.

>>>>

Unlike Bitcoin, transactions increment and decrement account balances; they do
not directly consume the output of other transactions. Transactions are also
used to setup and modify trustlines. To prevent replay attacks, accounts and
transactions have sequence numbers; a transaction is only valid if the Sequence
number is exactly one greater than the last-valided transaction from the same
account. Additionally an optional \texttt{AccountTxnID} field is available for use
within transactions; the transaction is only valid if the sending account's
previously-sent transaction matches the provided hash.
